worrms
======

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Build Status](https://travis-ci.org/ropensci/worrms.svg?branch=master)](https://travis-ci.org/ropensci/worrms)
[![codecov](https://codecov.io/gh/ropensci/worrms/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/worrms)
[![rstudio mirror downloads](http://cranlogs.r-pkg.org/badges/worrms)](https://github.com/metacran/cranlogs.app)
[![cran version](http://www.r-pkg.org/badges/version/worrms)](https://cran.r-project.org/package=worrms)

`worrms` is a R client for the World Register of Marine Species

* [World Register of Marine Species (WoRMS)](http://www.marinespecies.org/)
* [WoRMS REST API docs](http://www.marinespecies.org/rest/)

## Installation

More stable CRAN version

```{r eval=FALSE}
install.packages("worrms")
```

Development version

```{r eval=FALSE}
devtools::install_github("ropensci/worrms")
```

```{r}
library("worrms")
```

## get records

by date

```{r}
wm_records_date('2016-12-23T05:59:45+00:00')
```

by a taxonomic name

```{r}
wm_records_name(name = 'Platanista gangetica')
```

by many names

```{r}
wm_records_names(name = c('Platanista gangetica', 'Coryphaena'))
```

by common name

```{r}
wm_records_common(name = 'clam')
```

using the TAXMATCH algorithm

```{r}
wm_records_taxamatch(name = 'Platanista gangetica')
```


## Meta

* Please [report any issues or bugs](https://github.com/ropensci/worrms/issues).
* License: MIT
* Get citation information for `worrms` in R doing `citation(package = 'worrms')`
* Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md).
By participating in this project you agree to abide by its terms.
